### 2017-11-22 Docs/Thesis/docs/appendix/appendixE.tex
IMPORTANT: vou fazer algumas alterações, e tudo pode parar de funfar kkk -> preciso passar a interface ethernet como argumento para cada thread
thesis update, ch5 and ch6
update on the thesis text

\chapter{Publications}

\section{IX DCA/FEEC/University of Campinas (UNICAMP) Workshop (EADCA)}
\includepdf[pages=-]{figures/apE/eadca-article2016.pdf}

\section{X DCA/FEEC/University of Campinas (UNICAMP) Workshop (EADCA)}
\includepdf[pages=-]{figures/apE/eadca-article2017.pdf}

\section{Generic Paper}
\includepdf[pages=-]{figures/apE/paper.pdf}

>>>>

\chapter{Publications}
\label{ap:publications}

\begin{itemize}
	\item IX DCA/FEEC/University of Campinas (UNICAMP) Workshop (EADCA
	\item X DCA/FEEC/University of Campinas (UNICAMP) Workshop (EADCA)
	\item Using BIC and AIC for Ethernet traffic model selection. Is it worth?
	\item SIMITAR: realistic and autoconfigurable traffic generation
\end{itemize}

\includepdf[pages=-]{figures/apE/eadca-article2016.pdf}

\includepdf[pages=-]{figures/apE/eadca-article2017.pdf}

\includepdf[pages=-]{figures/apE/paperAicBic.pdf}

\includepdf[pages=-]{figures/apE/paperSimitar.pdf}

%\section{Generic Paper 3}
%\includepdf[pages=-]{figures/apE/paper3.pdf}

### 2017-11-22 Docs/Thesis/docs/appendix/todo.tex
update on the thesis text

Liks úteis:

>> http://www.backtrack-linux.org/forums/showthread.php?t=8740

>> https://sudks.wordpress.com/2016/04/27/tools-traffic-networking/

>> http://www.linuxlinks.com/article/2012042806090428/BenchmarkTools.html

>> http://uperf.org/

@@

\section{Chapter 3 - Architecture}

\section{Chapter 4 - Modeling}

\section{Chapter 5 - Prof of concepts}

\section{Chapter 6 - Usage cases}

\section{Chapter 7 - Conclusion}

>>>>

Liks úteis: 
http://www.backtrack-linux.org/forums/showthread.php?t=8740
https://sudks.wordpress.com/2016/04/27/tools-traffic-networking/
http://www.linuxlinks.com/article/2012042806090428/BenchmarkTools.html
http://uperf.org/

@@

### 2017-11-22 Docs/Thesis/docs/chapter3.tex
update on the thesis text

\textbf{Session-layer}: At the session layer, we use a deterministic approach for evaluating times between files and the actual file transference, the OFF and ON times of a packet train model, respectivaly. We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.  We develop an algorithm called \textit{calcOnOff} responsible for estimating these times. It also determines the number of packets and bytes transferred by each file. Since the on times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms. We did this, first because ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators. Second, because in the case of just one packet, the ON time would be zero. OFF times, on the other hand, are defined by the constant \texttt{m\_session\_cut\_time}. If the time between packets of the same flow is larger than this, we consider it belonging to a different file, so it is a Session OFF time. In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} (30 seconds) \textcolor{red}{<<<<pode mudar, calibrar>>>>}.
The control of ON/OFF periods is made by the \texttt{NetworkFlow} class.

>>>>

\textbf{Session-layer}: At the session layer, we use a deterministic approach for evaluating times between files and the actual file transference, the OFF and ON times of a packet train model, respectivaly. We choose a deterministic model because in this way we can express diurnal behavior\cite{harpoon-paper}.  We develop an algorithm called \textit{calcOnOff} responsible for estimating these times. It also determines the number of packets and bytes transferred by each file. Since the on times will serve as input for actual traffic generators, we defined a minimum acceptable time for on periods equals to 100 ms. We did this, first because ON times can be arbitrary smalls, and they could be incompatible with acceptable ON periods for traffic generators. Second, because in the case of just one packet, the ON time would be zero. OFF times, on the other hand, are defined by the constant \texttt{m\_session\_cut\_time}. If the time between packets of the same flow is larger than this, we consider it belonging to a different file, so it is a Session OFF time. In this case, we use the same value of the constant \textit{Request and Response timeout} of Swing\cite{swing-paper} (30 seconds).
The control of ON/OFF periods is made by the \texttt{NetworkFlow} class.
